A novel distributed nature-inspired algorithm for solving optimization problems\thanks{Supported by TECNOLÓGICO NACIONAL DE MÉXICO (TecNM).}

### 2021-09-30 paper.tex
Work in progress
Introduction update

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective, where each process must wait for the previous task to finish
before continuing. Some architectures address this issue, what distinguishes
us, is that our proposal presents an algorithm designed in its entirety as a
native solution in the cloud, fully distributed, where its processes are
executed in parallel and asynchronously. This technique makes it easy to scale
the computing power according to the complexity required by the problem.

@@

In this research, we seek to demonstrate that it is possible to evolve a
population of individuals, similar to a Genetic Algorithm (GA), using a
distributed, parallel, and asynchronous methodology.

\section{Description} 
% Description of the sections of the Paper
% We structure this research paper as follows

We present the description of the following sections in our research paper.

\begin{description}  % When enumerating with description, bullet alternatives: cdot, bullet, ast
    \item[$\cdot Background$] We do a brief explanation of our motivation for this research.
    \item[$\cdot Proposal$] We present an algorithm inspired by the Life-Cycle of animal species.
    \item[$\cdot Experiments$] We specify our experimental setup, configuration, and results.
    \item[$\cdot Discussion$] We analyze and describe some of our research findings.
    \item[$\cdot Conclusions$] We present some inferences based on our experiments' results.
    \item[$\cdot References$] We enumerate the references for our research paper.
\end{description}

>>>>

One of the problems that we have identified in this research is that most
bio-inspired algorithms are designed with a traditionally sequential
perspective [X-Z], where each process must wait for the previous task to finish
before continuing. Some architectures address this issue, what distinguishes
us, is that our proposal presents an algorithm designed in its entirety as a
native solution in the cloud, fully distributed, where its processes are
executed in parallel and asynchronously. This technique makes it easy to scale
the computing power according to the complexity required by the problem.

@@

The main contribution of the paper is to design and create a new algorithm with
the purpose to demonstrate that it is possible to evolve a population of
individuals, similar to a Genetic Algorithm (GA), using a distributed,
parallel, and asynchronous methodology by implementation and testing of the
algorithm.

We present the description of the following sections in our paper. First, we do
a brief explanation of our motivation for this research in section 2, next, we
present our algorithm inspired by the Life-Cycle of animal species in section
3, followed by our experimental configuration and results in section 4, then we
analyze and describe some of our research findings in section 5, and we
finalize by presenting some inferences based on our experiments' results in
section 6.
